---
title: "Weight of Fish"
author: "Michelle Benavides"
date: "July 19, 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
fishdata<-read.csv(file = "Fish.csv")
```

# Predicting Fish Weight


## Perch

```{r}
FishPerch<-filter(fishdata, Species == "Perch")
FishPerch<-select(FishPerch, -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishPerch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

The best regressor model is the one with the Height and Weight variables as its two regressors. The second best regressor model is the one with Length3, Height, and Weight as the regressor variables. 

## Pike

```{r}
FishPike<-filter(fishdata, Species == "Pike")
FishPike<-select(FishPike, -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishPike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

The best regressor model is the one with the Length1, Length2, Length3, Height, and Weight variables as its two regressors. The second best regressor model is the one with Length1, Length3, Height, and Weight as the regressor variables. 

## Roach

```{r}
FishRoach<-filter(fishdata, Species == "Roach")
FishRoach<-select(FishRoach, -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishRoach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

The best regressor model is the one with the Length3 and Weight variables as its two regressors. The second best regressor model is the one with Weight alone as the regressor variable. 

## Final Summary Statements